Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-11 paper.tex
remove unet, fix training regime, add shabbyreal experiment data

Another new dataset --- \emph{ShabbyReal} --- was produced as part of the larger \emph{ShabbyPages} corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper.  \emph{ShabbyReal} is fully out-of-distribution for the models in our experiments, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.

\subsection{Training Regime}
Training of the UNet model proceeded for 600 epochs, learning features from 1050 patches of 500x500 pixels.

The NAFNet was given a much larger sample to learn from: 10 square patches 400 pixels to a side were used to train this instance, across just 16 epochs.

Both models were trained with mean squared error as the loss function, using the Adam optimizer, and evaluated with the mean average error metric.

\subsection{Results}
Sample predictions from each model on the validation task are presented in Table 1. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

\begin{figure}\label{fig4}
\includegraphics[width=\textwidth]{figures/sidebyside.png}
\caption{Validation images (left), with the images predicted by the ShabbyPages_NAFNet (center) and ShabbyPages_NAFNet_large (right) models.}
\end{figure} %[TODO: can we show this a better way?]

To compare the models' performance on the validation task, we considered the following metrics:
\begin{enumerate}
\item Root mean square error (RMSE)
\item Structural similarity index (SSIM)
\item Peak signal-to-noise ratio (PSNR)
\end{enumerate}

\begin{table}
\centering
\caption{Denoising performance on \emph{ShabbyReal} validation task}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Metric & Score \\
\hline
SSIM & \\
PSNR & \\
RMSE & \\
\hline
\end{tabular}
\end{table}

[TODO: add numbers and interpretation]
\section{Robustness Testing}
In this section, we examine the use of \emph{Augraphy} to add noise which challenges existing models.

>>>>

Another new dataset --- \emph{ShabbyReal} --- was produced as part of the larger \emph{ShabbyPages} corpus \cite{ref_ShabbyPages}; this data was manually produced by applying sequences of physical operations to real paper. \emph{ShabbyReal} is fully out-of-distribution for this experiment, and also has a very high degree of diversity, providing good conditions for evaluating \emph{Augraphy}'s effect.

\subsection{Training Regime}
The NAFNet was given a large sample to learn from: for each image in the ShabbyPages set, we sampled ten patches of 400x400 pixels, using these to train the instance across just 16 epochs.

The model was trained with mean squared error as the loss function, using the Adam optimizer and cosine annealing learning rate scheduler, then evaluated with the mean average error metric.

\subsection{Results}
Sample predictions from the model on the validation task are presented in Figure \cite{fig:shabbyreal_denoising}. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

To compare the model's performance on the validation task, we considered the root mean square error (RMSE), structural similarity index (SSIM), and peak signal-to-noise ratio (PSNR) metrics.

\begin{table}
\centering
\caption{Denoising performance on \emph{ShabbyReal} validation task}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Metric & Score \\
\hline
SSIM & 0.71\\
PSNR & 32.52\\
RMSE & 6.52\\
\hline
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth]{figures/shabbyreal_denoised.png}
\caption{Sample \emph{ShabbyReal} noisy images (left) and their denoised counterparts (right).}
\label{fig:shabbyreal_denoised}
\end{figure}

As can be seen in  Figure \cite{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.

\section{Robustness Testing}
In this section, we examine the use of \emph{Augraphy} to add noise which challenges existing models.
